The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-11 exp-resurgence.tex
Keep arguing that special solutions have asymptotic expansions

\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$. Let's use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.

@@

For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$. In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3. The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
and the perturbation
%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
\color{SlateBlue}
\begin{itemize}
\item Prove Theorem~3 using Picard iteration, using the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
given by an arbitary point $b \in \Omega_\alpha$ as our initial guess.
\item This expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, makes it clear that the prototype solution belongs to $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
\item The operator $\volterra^\alpha$ preserves the intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$. Hence, the Picard iteration sequence must lie in this subspace.
\item We know from Lemma~\ref{lem:shifted_holo_closed} that the intersection of $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter. Hence, the solution $\psi_\alpha$ that Picard iteration converges to must also lie within this subspace.
\item Use Laplace transforms of truncated power series for $\psi_\alpha$ to show that $\Psi_\alpha$ has an asymptotic series?
\end{itemize}
\color{BlueViolet}

@@

\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation 
\begin{equation}\label{eqn:standard ODE}
\mathcal{P}\Psi=0
has a unique solution $\Psi_\alpha$ in the affine subspace

@@

As a consequence of Theorem~4 \cite{reg-sing-volterra}, after rescaling by a constant, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace

>>>>

\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$. Let's use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.

@@

Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$. We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve. This is equivalent to solving the inhomogeneous equation
\begin{equation}\label{eqn:inhomog-volterra}
\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
\end{equation}
The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough. It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$. More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration. Defining
\begin{align*}
\solptb^{(0)} & = \softpart^\alpha \solproto \\
\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
& \;\;\vdots
\end{align*}
we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution.

In \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
which shows that it lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]
and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself. It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies within the intersection of $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of the latter. The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$. Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.

%%Consider any $\rho > \tau$, recalling our assumption that $\tau > 0$. We know from Propositions \textcolor{orange}{\tt prop:smoothing} 9 and \textcolor{orange}{\tt prop:get-contraction} 10 of \cite{reg-sing-volterra} that $\softpart^\alpha$ maps
%%\[ \singexp{\tau-1}{\Lambda}(\Upsilon) \to \singexp{\tau}{\Lambda}(\Upsilon) \]
%%continuously and $\volterra^\alpha$ contracts $\singexp{\rho-1}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough. Under the same conditions, by working with Taylor series, we can show that $\softpart^\alpha$ maps
%%\[ \zeta^{\tau-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau}\,\mathcal{O}(\pi \Upsilon) \]
%%and $\volterra^\alpha$ maps $\zeta^{\rho-1}\,\mathcal{O}(\pi \Upsilon)$ to itself.
\color{SlateBlue}
\begin{itemize}
\item Prove Theorem~3 using Picard iteration, using the {\em prototype solution}
\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
given by an arbitary point $b \in \Omega_\alpha$ as our initial guess.
\item This expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, makes it clear that the prototype solution belongs to $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
\item The operator $\volterra^\alpha$ preserves the intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$. Hence, the Picard iteration sequence must lie in this subspace.
\item We know from Lemma~\ref{lem:shifted_holo_closed} that the intersection of $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter. Hence, the solution $\psi_\alpha$ that Picard iteration converges to must also lie within this subspace.
\color{SteelBlue}
\item \textbf{[still to do]} Use Laplace transforms of truncated power series for $\psi_\alpha$ to show that $\Psi_\alpha$ has an asymptotic series?
\end{itemize}
\color{BlueViolet}

@@

%%%\color{Maroon}
%%%\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
%%%Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation 
%%%\begin{equation}\label{eqn:standard ODE}
%%%\mathcal{P}\Psi=0
%%%\end{equation}
%%%has a unique solution $\Psi_\alpha$ in the affine subspace
%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
%%%\end{theorem}
%%%\begin{proof}

@@

%%%As a consequence of Theorem~4 \cite{reg-sing-volterra}, after rescaling by a constant, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
%%%\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
%%%of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$. The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$. It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
%%%\end{proof}
